Notes on Perturbational Quantities

### 2008-08-05 docs/pert_notes/paper.tex
typo
messing with the marginpars

\MarginPar{You could argue that including a time-lagged $\eta_\rho$ source term would 
decrease the error, but Ann has convinced me that this term isn't necessary.}  
This term is used to advect $\rho_0$ in advect\_base and to compute $\eta_\rho$, which will 
be used in correct\_base.

@@

\MarginPar{Does $\psi$ need to be included in the force?}

@@

We define $(\rho h)_0^{(1)} = \overline{(\rho h)^{(1)}}$  and 
(\ref{rhohprime equation}) as the forcing.\\ \\

@@

to sync up $(\rho h)_0$ after the thermal diffusion step.

@@

We would like to update the non-forcing part of the enthalpy equation analogously to
Section \ref{Advancing rhoX_k}

@@

- \nabla\cdot\left[(\rho h)_0^{n+\half,{\rm pred}}w_0\right].

>>>>

This term is used to advect $\rho_0$ in advect\_base and therefore must also be used 
to compute $\eta_\rho$, which will be used in correct\_base.

@@

\MarginPar{Does $\psi$ need to be included in the force?  I have written it in the base state equation for now, even though neither the base state or perturbational edge state prediction in the code uses $\psi$.  How about evolving density first,  then computing a time-centered $\psi$ to be used as the energy forcing?}

@@

@@

to sync up $(\rho h)_0$ after the thermal diffusion step.\\ \\
{\bf What I'd like to do:}  Define $(\rho h)_0^{(1)} = \overline{(\rho h)^{(1)}}$  and 
(\ref{rhohprime equation}) as the forcing.

@@

- \nabla\cdot\left[(\rho h)_0^{n+\half,{\rm pred}}w_0\eb_r\right].
{\bf What we would do to be consistent with density:} We would like to update the 
non-forcing part of the enthalpy equation analogously to Section \ref{Advancing rhoX_k}

@@
